### 2017-10-30 manuscript.rmd
added new library summary stats, xtable

@@

>>>>

	#summary statistics for libraries

	summary_stats = read.table("Library_summary.csv", header=TRUE, sep=",")
	names(summary_stats)<-c("Species","Mean insert size (bp)","Insert size standard deviation","Number of read pairs","Percent kept after rRNA removal","Percent kept after assembly","Adapter fails","Quality fails","Base Composition fails","Total assembled transcripts","Coding transcripts")
	specimen_data = read.csv("Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Collection date","Specimen id","Depth","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")
```

@@

xtable_summary<-xtable(summary_stats,auto=TRUE)
align( xtable_summary ) <- c('l|',rep('p{0.5in}',ncol(summary_stats)) )
print(xtable_summary, scalebox=0.7, include.rownames=FALSE)
